---
title: "DrugUsers"
author: "Monique Powell"
date: "Nov 19, 2019"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
avast <-read.csv(file="avastivironal.csv",header=TRUE)
avastf <- filter(avast,sex=="gal")
avastM <- filter(avast, sex=="guy")
avastG <- filter(avast, LGBTQ=="gay")
avastD <- filter(avast, DrugUser=="yes")
```



# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative aides (abacavirinol) is under test in clinical trials. We will analyze the effectiveness of this drug across the board. We will consider population subgroups by gender, such as male and female, drug use, and sexual orientation as well as group which will include everyone.
For the variable analysis we will use graphical method, such as a bar chart that will provide a way to make a visual distinction between the treatment and infected responses  as well as a numerical method, such as a table1 which will provide the percentage breakdown as well as a chi-square test of independence for an inferential result which will provide a p-value providing whether or not if there any evidence if there's a relationship between getting Aides and taking avastivironal.


$H_O$: There is no relationship between getting Aides and taking avastivironal.

$H_1$: There is a relationship between getting Aides and taking avastivironal.


# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->


We will use a bar chart for the graphical that will provide us a way to make a visual distinction between the treatment and infected responses, and a table1 for a numerical breakdown.
To test if there is a statistically significant correlation between infected and treatment, we will use a chi-squared test of independence.


#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

```{r}
barchartGC(~infected + treatment, data=avastD)
barchartGC(~infected + treatment,data=avast,type= "percent")
```

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->


The bar chart shows that those who took placebo recieved Aides full less then those who didn't take the treatment which suggest the drug is working.


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->


```{r}
table1 <- xtabs(~infected + treatment, data=avastD)
rowPerc(table1)
colPerc(table1)
```


The numerical results tells us that among those who took placebo about 24% got Aides, whereas those who didn't take the treatment about 76% got Aides which suggest there a better chances of not receiving Aide by taking the treatment than not taking it.


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

$H_O$: There is no relationship between getting Aides and taking avastivironal.

$H_1$: There is a relationship between getting Aides and taking avastivironal.

The  P-Value = 4.23e-08, which is lower than the conventional threshold of 0.05, meaning we can reject the null hypothesis that the treatment seem to be working, because among those who took placebo about 24% got Aides, whereas those who didn't take the treatment about 76% got Aides.


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The graphical result provided the effectiviness of the new aid drug (abacavirnol)on the general population; the visual distinction between the treatment and injected suggested that those who took placebo recieved Aides full more than those who didn't take the treatment. The numerical result provided the effecyiviness of abacavirnol on the general population; which provided the percentage breakdown that revealed that among those who took placebo about 24% got Aides, whereas those who didn't take the treatment about 76% got Aides, which suggest that the drug is effective for those who used the drug. The chi-square test of independence was used for an inferential result that provided a p-value such as 4.23e-08 which points out whether or not if there any evidence; which in this case it appears that there's a relationship between getting Aides and taking avastivironal because the P-Value = 4.23e-08, which is lower than the conventional threshold of 0.05, meaning we can reject the null hypothesis that the treatment seem to be working .  The sample estimates odds ratio equals   0.3534128 compares to 1:1 ratio for those who use placebo.
